Tampering Detection In Low-Power Smart Cameras

### 2015-05-27 paper.tex
Messa immagine indicatori nel paper
sistemata reference a figura 2

As shown in Figure REFERENCE\_TODO.a), tampering results in outliers in the sequence of indicators. Detecting these outliers is not straightforward, since indicators heavily fluctuates in normal conditions because of short-term variations in the depicted scene or illumination changes. For outlier-detection purposes~\cite{Chandola2009}, it is more convenient to operate on sequences of independent and identically distributed (i.i.d.) values, where outliers can be detected by density-based methods or simply by confidence regions that is what we considered in our algorithm. Unfortunately, trends or deterministic variations in the indicator sequences are not easy to compensate because of unpredictable evolutions of the scene.

@@

\begin{figure}[tb]
\centering
\label{fig:indicatori} 
\includegraphics[width=1\linewidth]{Immagini/indicatori}
\caption{Behavior of the average norm of the gradient \textbf{(a)} and its detrending \textbf{(b)} in a sequence with a defocus event.
The tampering event come at $t = 600$.
As illustrated in \textbf{(a)}, even in the case in which there aren't tampering events, there is nonstationarity.
Detrending is done in order to preserve stationarity in normal situations.
Considering the detrending \textbf{(b)} persistent changes become instantaneous:
in particular there is a peak in the instant in which tampering begins.}
\end{figure}

@@

\section{Experiments}\label{sec:experiments}
The proposed algorithm has been implemented in MATLAB, and has been tested on two datasets.
The first one refers to frame sequences taken from webcams recording some parts of cities (as in Figure \ref{fig:sequences}(a)), where we have introduced some synthetically generated tampering events:
defocus has been simulated using gaussian filters (\ref{fig:sequences}(b)), while displacement has been created with concatenation of similar frame sequences (Figure \ref{fig:sequences}(c)).
In some cases these sequences contained real tampering events, as in Figure \ref{fig:sequences}(d).\\
\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/sequenze}
\caption{Sequences taken from webcams: \textbf{(a)} no tampering events; \textbf{(b)} defocus event on 4-th and 5-th frames, created using gaussian filtering; \textbf{(c)} displacement event on 4-th and 5-th frames, created using concatenation between similar sequences; \textbf{(d)} real displacement event on 4-th frame.}
\label{fig:sequences}
\end{figure}
The second dataset was taken using a Raspberry Pi Model B+, with its camera module, and the tampering was introduced by moving the device or putting water on the camera.\\
Four figures of merit have been suggested to assess the performance of the proposed algorithm:\\
\begin{description}
	\item[TP]  True positives. It measures the number of tampering events correctly detected by the algorithm.\\ 
	\item[TN]  True negatives. It measures the number of frames without tampering that are not detected by the algorithm. \\ 
	\item[FP]  False positives. It measures the number of tampering events erroneously detected by the algorithm.\\ 
	\item[FN]  False negatives. It measures the number of tampering events not detected by the algorithm. \\ 
\end{description} 
These indicators are computed varying the parameter $\gamma$, which defines the thresholds for the one-shot monitoring. 
This permits us to generate \textit{ROC curves}, where on the x-axis there is:
\[1-\text{SPECIFICITY}_\gamma = 1-\frac{\text{TN}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}=\frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma},\]
while on th y-axis there is:
\[\text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}.\]
The construction of these curves permits us to make a comparison with respect to other methods.
In particular the alternative approaches that we have considered working:
\begin{itemize}
\item considering the whole scene for the features computation;
\item considering adaptive region, as described in Section \ref{sec:propSol}, for the feature computation;
\item considering voronoi regions \cite{aurenhammer1991voronoi}, which are easier to compute with respect to our solution but don't consider the scene content, for the feature computation.
\end{itemize}

>>>>

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{Immagini/indicatori}
\caption{Behavior of the average norm of the gradient \textbf{(a)} and its detrending \textbf{(b)} in a sequence with a defocus event.
The tampering event come at $t = 600$.
As illustrated in \textbf{(a)}, even in the case in which there aren't tampering events, there is nonstationarity.
Detrending is done in order to preserve stationarity in normal situations.
Considering the detrending \textbf{(b)} persistent changes become instantaneous:
in particular there is a peak in the instant in which tampering begins.}
\label{fig:indicatori} 
\end{figure}

As shown in Figure \ref{fig:indicatori}(a), tampering results in outliers in the sequence of indicators. Detecting these outliers is not straightforward, since indicators heavily fluctuates in normal conditions because of short-term variations in the depicted scene or illumination changes. For outlier-detection purposes~\cite{Chandola2009}, it is more convenient to operate on sequences of independent and identically distributed (i.i.d.) values, where outliers can be detected by density-based methods or simply by confidence regions that is what we considered in our algorithm. Unfortunately, trends or deterministic variations in the indicator sequences are not easy to compensate because of unpredictable evolutions of the scene.

@@

@@

\section{Experiments}\label{sec:experiments}
The proposed algorithm has been implemented in MATLAB, and has been tested on two datasets.
The first one refers to frame sequences taken from webcams recording some parts of cities (as in Figure \ref{fig:sequences}(a)), where we have introduced some synthetically generated tampering events:
defocus has been simulated using gaussian filters (Figure \ref{fig:sequences}(b)), while displacement has been created with concatenation of similar frame sequences (Figure \ref{fig:sequences}(c)).
In some cases these sequences contained real tampering events, as in Figure \ref{fig:sequences}(d).\\
\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/sequenze}
\caption{Sequences taken from webcams: \textbf{(a)} no tampering events; \textbf{(b)} defocus event on 4-th and 5-th frames, created using gaussian filtering; \textbf{(c)} displacement event on 4-th and 5-th frames, created using concatenation between similar sequences; \textbf{(d)} real displacement event on 4-th frame.}
\label{fig:sequences}
\end{figure}
The second dataset was taken using a Raspberry Pi Model B+, with its camera module, and the tampering was introduced by moving the device or putting water on the camera.\\
Four figures of merit have been suggested to assess the performance of the proposed algorithm:\\
\begin{description}
	\item[TP]  True positives. It measures the number of tampering events correctly detected by the algorithm.\\ 
	\item[TN]  True negatives. It measures the number of frames without tampering that are not detected by the algorithm. \\ 
	\item[FP]  False positives. It measures the number of tampering events erroneously detected by the algorithm.\\ 
	\item[FN]  False negatives. It measures the number of tampering events not detected by the algorithm. \\ 
\end{description} 
These indicators are computed varying the parameter $\gamma$, which defines the thresholds for the one-shot monitoring. 
This permits us to generate \textit{ROC curves}, where on the x-axis there is:
\[1-\text{SPECIFICITY}_\gamma = 1-\frac{\text{TN}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}=\frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma},\]
while on th y-axis there is:
\[\text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}.\]
The construction of these curves permits us to make a comparison with respect to other methods.
In particular the alternative approaches that we have considered working:
\begin{itemize}
\item considering the whole scene for the features computation;
\item considering adaptive region, as described in Section \ref{sec:propSol}, for the feature computation;
\item considering voronoi regions \cite{aurenhammer1991voronoi}, which are easier to compute with respect to our solution but don't consider the scene content, for the feature computation.
\end{itemize}
